\section{Evaluation}
The below chapter is going to evaluate the project as a whole unit covering a range of different scenarios in an overview and also highlighting what was learnt from the project.

\subsection{What went well} %Project successes
Starting with the successes of the project a wide variety went well the first key thing is a majority of the system was completed and the final result is an indoor mapping system with path finding albeit missing the location calculation it's still a great result for a project made in a short space of time. The final project has resulted in the base infrastructure and prototype for an indoor mapping solution that could plausibly be turned into a business especially if the location calculation problem is fixed at a later date. Both the web application and android application turned out well and looked like the initial designs and overall the result is excellent quality with a maintainable code base.

\subsection{The non-complete and why}
There is a range of elements of the system that where not complete the main reason for this is the project being large and ambitious from the start some of the non-complete items where not done because of x whereas other's where done due to time constraints. The non complete requirements can be seen by looking at the appendix for the user stories, additionally another table exists in the appendix highlighting pass/fail on each requirement number.

\subsection{System limitations} 
Rectangle storage of rooms
Walls are included in the size of a room
No Z-co-ordinate only x,y. Floor's are detected by localised sensors which is untested due to environmental restraints.

\subsection{What I'd do differently next time}
Some extra design layouts to pre-vent reworking
Some extra time spent on scoping, project left scope and got more complicated too quickly, meaning some work wasn't finished
Don't jump straight into react/new technologies

\subsection{Future Work}
Re-work the web app refactoring to use redux

\subsection{What I learnt} % Project Takeaway
One key thing I learnt during the development of the project was about some more modern web development namely react and it's integration with API's. Before this project a significant portion of my dynamic website development was done via Java Servlets or done with PHP. Doing this project taught me a great deal about react to the extent where I can now make a basic application proficiently using react.

Another key element I learnt about was from the custom pixel based rendering system I wrote as mentioned in \citetemp 

React
Things about 2 rendering pixel by pixel IE: Line drawing algorithms, Filled Polygon rendering etc.
About JWT tokens
About indoor positioning
loads of other stuff

\subsection{Conclusion}
